%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer}
    {Bitu}
    {Beijing, China}
    {Mar. 2018 - PRESENT}
    {
      \begin{cvitems}
        \item {Building and optimizing recommender system}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Algorithm Engineer}
    {Didi Chuxing}
    {Beijing, China}
    {Mar. 2016 - Feb. 2018}
    {
      \begin{cvitems}
        \item {Worked on SDP(Supply-Demand Prediction) project. Designed and built demand regression and supply-demand gap classification predictive
model. Mined business features and implemented different state-of-art models to optimize model performance. Built and maintained SDP
service used for Dispatching and Intelligent Marketing.}
        \item {Worked on Intelligent Marketing project. Designed and built user-activation, user-loss and bubble-order(like CTR) predictive model used for
user targeting in Intelligent Marketing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Mining Engineer}
    {Meituan}
    {Beijing, China}
    {Jul. 2014 - Feb. 2016}
    {
      \begin{cvitems}
        \item {Worked on hotel ranking system. Implemented and maintained microservice of ranking system used for large-scale, real-time, personalized
hotel searching. Designed and built machine learning pipeline for CTR and CVR model. Mined business features and implemented different
state-of-art models to optimize CTR prediction. Resulted in paying rate increasing from 6\% to 14\%.}
        \item {Worked on channel traffic monitoring system. Built ETL pipeline to collect critical user actions like impression, click, order and refund and
calculate according conversion rates at different stages. Presented important statistic results with dashboards and automated reports.}
        \item {Gain S score(<3\%) twice in performance evaluations.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Mining Engineer Intern}
    {Meituan}
    {Beijing, China}
    {Nov. 2013 - Apr. 2014}
    {
      \begin{cvitems}
        \item {Worked on hotel customer profile mining. Used stats and machine-learning to find user order patterns in data.}
        \item {Worked on cheating device detection.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Develop Engineer Intern}
    {Microsoft}
    {Beijing, China}
    {May. 2013 - Nov. 2013}
    {
      \begin{cvitems}
        \item {Participated in developing Bugsearcher(an internal tool) and it’s monitoring service.}
        \item {Transplanted Ford’s open source product AppLink from POSIX to Windows.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
